Hydras \& Co.

### 2022-01-15 doc/gaia-chapter.tex
try to use DejaVu Sans Mono

\subsubsection{A few constants}
For each constant: $0$, $1$, \dots, $n$ and ω, ω again, we prove
that the \texttt{hydras}' definition refines \texttt{gaia}'s.
\inputsnippets{T1Bridge/constantRefs}

>>>>

\subsubsection{A few constants}
For each constant: $0$, $1$, \dots, $n$ and $\omega$, we prove
that \texttt{hydras}' definition refines \texttt{gaia}'s.
\inputsnippets{T1Bridge/constantRefs}
